Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
edit

\citep{JingSuto02} report the twisting in their simulations.
They also find a universal radius where the alignment of the internal 
region (defined as the region with 2500 times the critical density) 
is perfect with the shell under consideration.
They blame it on high c/b and undecided vectors.
but in our case c/b increases monotonically with radius, and the
alignment with the disk is not monotonous. In our case this cannot be
the only explanation as the triaxiliaty correlation with the twist 
strongly depends on the radius.

@@

Our second results deals with the disk-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disk and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disk-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii, its strenght correlating strongly with halo
triaxiality measured at $0.12R_{200}$.

This makes that 
\citep{Debattista08} found a similar effect, but only at radii smaller
than the disk radius. At radii larger than the disk radius, they find,
the dark matter shells stop twisting.

>>>>

@@

Our second results deals with the disk-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disk and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disk-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii, its strenght strongly correlating with halo
triaxiality measured at $0.12R_{200}$.

\citep{Debattista08} reported a similar twisting effect, but only at radii smaller
than the disk radius. 
At radii larger than the disk radius, they find, the dark matter
shells stop twisting. 
\citep{JingSuto02} reported shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they the twisting as an artifact resulting from high values of the
$c/b$ ratios that make the determination of the medium axis boisy.
Could then high triaxility values explain the twisting as a result of
erratic axis directions? 
If the triaxiality were the main culprit behind the twisting, the
correlation between the two quantities should be constant at every
radii.
In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows and
almost perfect alignment between the stellar disk at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$
